Revisiting the Nos\'{e}-Hoover chain thermostat applied to the Rigid Bodies Molecular Dynamics

### 2017-04-01 rigid_bodies.tex
march 24
april1

\begin{abstract}
In Molecular Dynamics, sets of atoms collectively behaving as rigid bodies are often used to model entire molecules or parts thereof. Such a coarse-graining strategy eliminates degrees of freedom and admits larger time steps without abandoning the atomistic character of a model. In this paper, we rely on a particular factorization of the rotation matrix to simplify the mechanics of systems containing rigid molecules. Then, we present equations of motion and devise time-reversible, measure-preserving integrators for both microcanonical (NVE) and canonical (NVT) dynamics. We also develop new expressions for computing the virial pressure of rigid-body systems under periodic boundary conditions. Finally, simulations of liquid water are employed to analyze the numerical aspects of the proposed methodology.
\end{abstract}

@@

Molecular Simulation is the computacional realization of Statistical Mechanics\cite{Tuckerman2010} that makes possible a microscopic insight into complex physical phenomena. To mimic ``real'' systems, numerical approximation are required under which certain Statistical Mechanics laws cannot be assumed to be valid also in Molecular Simulation. For instance, it has already been shown that the unavoidable truncation errors associated with the numerical integration of the equations of motion in Molecular Dynamics disrupt the equipartition of energy, and as a consequence the temperature becomes an undefined property\cite{Eastwood_2010}. In a previous paper,\citep{Abreu_2017} we observed the same problem, but regarding the partition of the kinetic energy between translational and rotational degrees of freedom in Molecular Dynamics of rigid bodies in the microcanonical ensemble. That finding brough into question the method introduced by Kamberaj and co-workers\cite{Kamberaj2005} which, assuming equipartition, couples separate chains of Nos\'{e}-Hoover thermostats on the rotational and translational degrees of freedom and fails to reproduce the specified temperature for certain time step sizes.

@@

CÓDIGO: CHECAR FACTORIZACIÓN Y DELTA T DE LOS OPERADORES DE NHC

@@

It is not the purpose of this work to propose an optimal factorization scheme for the NVT dynamics, but rather to prove that a unique thermostat chain is capable of maintaining the average temperature at its specified value while providing the proper sampling of the canonical ensemble. First we present some results as first mented. That is, the proposed methods coupling to a single thermostat, while in Kamberaj the translational and rotational degrees of freedom are separatedly coupled. In Table~\ref{table:new_results}, it can be seen that the integrators proposed here, which are represented by the Eqs.~\eqref{eq:trotter_splitting_NHC} and ~\eqref{eq:modified_splitting}, systemcatically achive the specifed temperature, regardless of the time step size. By contrast, the numerical solver introduced by Kamberaj and co-workers\cite{Kamberaj2005} fails to yield the specified temperature for even the smaller time step size of 1 fs.

Resultados sobre o checkensemble: We report the results corresponding to that method, and since it is instructive to have a graphical insight, we also show some figures of the linear fitting. Given that the potential and kinetic energies are separable, the analysis can be made separately as follows.This last approach does not involve any binning of the energies, hence no discretization error is present. m-b distribution valid when equipartition of energy is satisfied.

@@

%\begin{equation}
%\label{eq:probability_ratio_kin}
%\frac{P_{kin}(E/\beta_2)}{P_{kin}(E/\beta_1)} = \frac{Q_{kin}(\beta_1)}{Q_{kin}(\beta_2)}  \exp\left[(-%\beta_2 - \beta_1)E_{kin}\right]
%\end{equation}
\end{document}

>>>>

%\begin{abstract}
%In Molecular Dynamics, sets of atoms collectively behaving as rigid bodies are often used to model entire molecules or parts thereof. Such a coarse-graining strategy eliminates degrees of freedom and admits larger time steps without abandoning the atomistic character of a model. In this paper, we rely on a particular factorization of the rotation matrix to simplify the mechanics of systems containing rigid molecules. Then, we present equations of motion and devise time-reversible, measure-preserving integrators for both microcanonical (NVE) and canonical (NVT) dynamics. We also develop new expressions for computing the virial pressure of rigid-body systems under periodic boundary conditions. Finally, simulations of liquid water are employed to analyze the numerical aspects of the proposed methodology.
%\end{abstract}

@@

Molecular Simulation is the computacional realization of Statistical Mechanics\cite{Tuckerman2010} that makes possible a microscopic insight into complex physical phenomena. To mimic ``real'' systems, numerical approximation are required under which certain Statistical Mechanics laws cannot be assumed to be valid. For instance, it has already been shown that the unavoidable truncation errors associated with the numerical integration of the equations of motion in Molecular Dynamics disrupt the equipartition of energy, and as a consequence the temperature becomes an undefined property\cite{Eastwood_2010}. In a previous paper,\citep{Abreu_2017} we observed the same problem, but regarding the partition of the kinetic energy between translational and rotational degrees of freedom in Molecular Dynamics of rigid bodies in the microcanonical ensemble. That finding brough into question the method introduced by Kamberaj and co-workers\cite{Kamberaj2005} which, assuming equipartition, couples separate chains of Nos\'{e}-Hoover thermostats on the rotational and translational degrees of freedom and fails to reproduce the specified temperature for certain time step sizes.

@@

%CÓDIGO: CHECAR FACTORIZACIÓN Y DELTA T DE LOS OPERADORES DE NHC

@@

It is not the purpose of this work to propose an optimal factorization scheme for the NVT dynamics, but rather to prove that a unique thermostat chain is capable of maintaining the average temperature at its specified value while providing the proper sampling of the canonical ensemble. First we present some results as first mented. That is, the proposed methods coupling to a single thermostat, while in Kamberaj the translational and rotational degrees of freedom are separatedly coupled. In Table~\ref{table:new_results}, it can be seen that the integrators proposed here, which are represented by the Eqs.~\eqref{eq:trotter_splitting_NHC} and ~\eqref{eq:modified_splitting}, systemcatically achive the specifed temperature, regardless of the time step size. By contrast, the numerical solver introduced by Kamberaj and co-workers\cite{Kamberaj2005} fails to yield the specified temperature for even the smaller time step size of 1 fs.
%Resultados sobre o checkensemble:

checkensemble:We report the results corresponding to that method, and since it is instructive to have a graphical insight, we also show some figures of the linear fitting. Given that the potential and kinetic energies are separable, the analysis can be made separately as follows.This last approach does not involve any binning of the energies, hence no discretization error is present. m-b distribution valid when equipartition of energy is satisfied.

@@

%\begin{equation}
%\label{eq:probability_ratio_kin}
%\frac{P_{kin}(E/\beta_2)}{P_{kin}(E/\beta_1)} = \frac{Q_{kin}(\beta_1)}{Q_{kin}(\beta_2)}  \exp\left[(-%\beta_2 - \beta_1)E_{kin}\right]
%\end{equation}
\end{document}
\grid
